Stack Safety as a Security Property

### 2020-07-09 main.tex
subsections in 6
Misc

%% Keywords
%% comma separated list
\keywords{Stack Safety, Micropolicy, Random Testing, RISC-V}  %% \keywords are mandatory in final camera-ready submission

@@

@@

  \paragraph{Adding Heap Safety}

    Heap safety, like stack safety, may be framed as a form of noninterference
    [cite Meaning of Memory Safety]. The above model describing safety of
    shared stack-allocated objects extends naturally to heap safety,
    complicated by the fact that these objects are not deallocated by returns,
    and therefore a function's privilege may increase or decrease after its
    entry point. For instance, if a callee allocates a heap object and returns
    the pointer to its caller, that object's addresses become accessible in
    contradiction to a contour computed at the caller's entry. So such an
    extension must enforce trace confidentiality and integrity properties
    separately on continuous segments of each call, with contours computed at
    each crossing between caller and callee.

>>>>

%% Keywords
%% comma separated list
\keywords{Stack Safety, Micropolicies, Random Testing\bcp{Really??}, RISC-V}  %% \keywords are mandatory in final camera-ready submission

@@

  \paragraph{Heap Safety as a Security Property}
\bcp{Talk about the relation.}
    Heap safety, like stack safety, may be framed as a form of
    noninterference\citet{DBLP:conf/post/AmorimHP18}. The above model
    describing safety of
    shared stack-allocated objects extends naturally to heap safety,
    complicated by the fact that these objects are not deallocated by returns,
    and therefore a function's privilege may increase or decrease after its
    entry point. For instance, if a callee allocates a heap object and returns
    the pointer to its caller, that object's addresses become accessible in
    contradiction to a contour computed at the caller's entry. So such an
    extension must enforce trace confidentiality and integrity properties
    separately on continuous segments of each call, with contours computed at
    each crossing between caller and callee.

@@
